Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-25 docs/thesis/chap-evaluation.tex
work on thesis
cleaned useless docs

\section{Comparison against other systems}
In this section we tried to compare our implementation of MASE(CDS) with the public available systems presented in the related work chapter. We judged if the fetched results of each system were relevant or not using the same criteria as for the previous section.  The systems were tested using Firefox 26.0
Table \ref{comparison_sw_table} presents the results of our test.

@@

The results are a little disappointing since from the eight evaluated instances, only MIaS and Symbolab seem to be working properly.

@@

\begin{longtable}{|c|c|c|}
\hline 
Expression Length (Number of leaf nodes)& Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
3 & 0.01195 & 2.65  \\ \hline
8 & 0.0142 & 9.97  \\ \hline
7 & 0.0129 & 9.165  \\ \hline
12 & 0.0194 & 15.15  \\ \hline
18 & 0.0201 & 29.5  \\ \hline
20 & 0.0245 & 27.75  \\ \hline
22 & 0.0264 & 32.4  \\ \hline
24 & 0.02502 & 32.1 \\ \hline

>>>>

\section{Comparison against other systems}
In this section we compared our implementation of MASE(CDS) with the public available systems presented in the related work chapter. We judged if the fetched results of each system were relevant or not using the same criteria as for the previous section.  The systems were tested using Firefox 26.0
Table \ref{comparison_sw_table} presents the results of our test.

@@

The first result about this evaluation is that only two different instances developed and running. The other ones seems to have been abandoned.

@@

%%
%\begin{longtable}{|m{3.5cm}|>
%{\centering\arraybackslash}m{3cm}|>
%{\centering\arraybackslash}m{3cm}|>
%{\centering\arraybackslash}m{5cm}|
%}
%\hline 
%\textbf{\LaTeX} & 
%\textbf{Presentation MathML} & 
%\textbf{Content MathML + Presentation Markups} & 
%\textbf{OpenMath}  \\ \hline
%%%

\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}|>
{\centering\arraybackslash}m{3cm}|>
{\centering\arraybackslash}m{3cm}|
}
\hline 
Expression Length (Number of leaf nodes)& Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
3 & 0.01195 & 2.65  \\ \hline
8 & 0.0142 & 9.97  \\ \hline
7 & 0.0129 & 9.165  \\ \hline
12 & 0.0194 & 15.15  \\ \hline
18 & 0.0201 & 29.5  \\ \hline
20 & 0.0245 & 27.75  \\ \hline
22 & 0.0264 & 32.4  \\ \hline
24 & 0.02502 & 32.1 \\ \hline
